Predicting FOMC Actions using NLP; Assesing the impact of matrix sparsity and regularization

### 2019-05-13 presentation/paperv2.tex
v2

\noindent For this study we used \textbf{CountVectorizer} (\textbf{TfiDf} can also be used, but it did not alter the conclustions of this study).
When are n-gram is applied to corpus it combinatorics diticates a large number of features will be generated and for a given feature, most of the column entries will
be zero, resulting in extremly sparse matricies.  The table below gives a measure of $\mbox{sparsity} = \frac{non-zero elements}{total elements}$ and 
the resulting number of elements in each n-gram generated matrix in the billions. In general stacking reduces the sparsity by a factor of 4 and
the matrix size by a factor of 5. The L1 matrix norm for all of the matricies ranged between 1200 to 1600.\\

@@

\subsection{Apply ML to Sparse Matricies generated from CountVectorizer}
<TODO>

>>>>

\noindent For this study we used \textbf{CountVectorizer} (\textbf{TfiDf} can also be used, but it did not alter the conclustions of this study).
When an n-gram is applied to corpus combinatorics diticates a large number of features will be generated and for a given feature, most of the column entries will
be zero, resulting in extremly sparse matricies.  The table below gives a measure of $\mbox{sparsity} = \frac{non-zero elements}{total elements}$ and 
the resulting number of elements in each n-gram generated matrix in the billions. In general stacking reduces the sparsity by a factor of 4 and
the matrix size by a factor of 5. The L1 matrix norm for all of the matricies ranged between 1200 to 1600.\\

@@

\subsection{Apply ML to Sparse Matricies generated from CountVectorizer}
\noindent
For this problem the large feature size relative to the the number of labels dicitates looking
at Bayesian approach or some from of L1 regularization (HW1 problem 2) to push a large number
of coefficients to zero.
\begin{itemize}

\item Naive Bayes
\begin{equation*}
P(A|x_1,x_2,...,x_n) = p(A)\prod_{i=1}^n p(x_i|A)
\end{equation*}

\item Logistic Lasso
\begin{equation*}
A = \prod_{i=1}^n p(x_i)^{y_i}(1-p(x_i))^{1-y_i}+ L1
\end{equation*}

\end{itemize}
